%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv}
\usepackage{multicol}
\usepackage{ragged2e}
\setlength{\columnsep}{1cm}
%----------------------------------------------------------------------------------------


\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Payton Wilkes}}}} % First name

	\vspace{6pt}

	{\Large Developer $\sim$ Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{Phone}{11}{1-435-730-2006}\\
    \icon{MapMarker}{11}{Ogden, Utah}\\

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Envelope}{11}{\href{mailto:Wilkespayton@gmail.com}{wilkespayton@gmail.com}}\\
    \icon{Github}{11}{\href{https://github.com/IMGradeE}{GitHub}}\\
\end{minipage}
\vspace{-10pt}
 \cvsect{Objective}

    \vspace{-8pt}
    %\RaggedRight
    \setlength{\parindent}{1.25em}
    I am looking for an employment opportunity in the field of Computer Science where I can expand on my skills as a programmer, software engineer, and leader.
    \setlength{\parindent}{0em}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.49\textwidth}
    \vspace{-\baselineskip}
\cvsect{Primary Interests}
\vspace{-6pt}
\begin{itemize}[itemsep=2pt,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=2em]
\item Service, Platform, and Workflow Automation
\item Applied Machine Learning \& Artificial Intelligence
\item Database Design and Maintenance
\item Cloud Computing \& Infrastructure
\item Platform Security \& Vulnerability Detection
\item Computational Efficiency and Process Optimization
\item Web \& Mobile Development
\item API Testing, Development, Integration \& Deployment.

\end{itemize}
\cvsect{Relevant Courses}\\
    \begin{minipage}[t]{.02\textwidth}
    \end{minipage}
    \hfill
     \begin{minipage}[t]{.98\textwidth}
    \textbf{Computer Science}
    \begin{itemize}[itemsep=3pt,topsep=4pt,parsep=0pt,partopsep=0pt, leftmargin=2em]
        \item Foundations of Computing
        \item Programming I
        \item Object Oriented Programming
        \item Computational Structures; Discrete - Mathematics
        \item Network Fundamentals \& Design
        \item Data Structures \& Algorithms
         \item Client Side Web Development
         \item Software Engineering I
         \item Intro to Database Design \& SQL
         \item Calculus I \\
         \texttt{SQL}\slashsep\texttt{Linux}\slashsep\texttt{Visual Studio}\slashsep \texttt{CLion}\\\texttt{C++ / C}\slashsep\texttt{Python}\slashsep\texttt{Java / JavaScript}\\\texttt{WireShark}\slashsep\texttt{CMake}\slashsep \texttt{Valgrind} \slashsep \texttt{WSL2}
    \end{itemize}
    \vspace{4mm}
    \textbf{General Education}
    \begin{itemize}[itemsep=3pt,topsep=4pt,parsep=0pt,partopsep=0pt, leftmargin=2em]
         \item Pre-Calculus; College Algebra and Trigonometry
         \item Intro to Statistics
         \item Intro to Engineering Culture
         \item Interpersonal \& Small Group Communication
    \end{itemize}
    \end{minipage}
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}
 \vspace{-\baselineskip}
    \cvsect{Education \& Affiliations}
 \begin{entrylist}
        \entry
    		{BS}
            {Computer Science:}
            {Weber State}
            { Enrolled, Full time since Jan 2022; \hspace{.13\textwidth}GPA: \textit{3.41} \\Graduating June 2025}
        \entry
            {CP}
    		{Programming Essentials:}
    		{Weber State}
            {Completed December 2023. \\GPA:\hspace{.692\textwidth} \textit{3.41}}
        \entry
    		{Member}
    		{American Mensa:}
    		{\href{https://www.us.mensa.org/}{MENSA}}
            {Qualifying score \textit{(WAIS-V)} \textbf{:} \hspace{.342\textwidth}\textit{135}\\ Member \#
            \hspace{.469\textwidth}\textit{200256130}}
    \end{entrylist}
    \vspace{-15pt}
    \cvsect{Projects}
    \begin{entrylist}
        \entry
    		{C++}
            {Sorting Algorithms}
            {\href{https://github.com/IMGradeE/Other_Uni_Projects/tree/CanonSortingAlgorithm}{GitHub link}}
            {Implementation of four common sorting algorithms}
            \entry
            {C++}
    		{Mock Technical Interview}
    		{\href{https://github.com/IMGradeE/MockInterview_Fall-2023https://github.com/IMGradeE/MockInterview_Fall-2023}{GitHub link}}
            {My responses to in class mock interview.}
        \entry
    		{C++}
    		{Hangman Game}
    		{\href{https://github.com/IMGradeE/Hangman_Fall-2022}{GitHub link}}
            {Console version of Hangman.}
        \entry
    		{Python}
    		{Game of NIM}
    		{\href{https://github.com/IMGradeE/GameOfNim_Spring-2022}{GitHub link}}
            {A game of NIM written in Python. Requires FFMPEG.}
    \end{entrylist}
    \vspace{-5pt}
    \cvsect{Skills}
\begin{minipage}[t]{.02\textwidth}
    \end{minipage}
    \hfill
     \begin{minipage}[t]{.98\textwidth}
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      C++, C, JavaScript, Java, SQL, Kotlin. Python, LaTeX, Markdown, CSS, HTML.
    \end{minipage}

    \vspace{2.5mm}
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Burp Suite, CMAKE, WSL, ValGrind, Git \& GitHub, Junit, Wireshark, Visual Studio, Clion.\\
    \end{minipage}
    \end{minipage}
    \cvsect{Soft Skills \& Attributes}
    \vspace{-20pt}
    \begin{itemize}[itemsep=2pt,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=2em]
        \item Interpersonal \& small group communication
        \item Abstract, Analytic \& Technical problem solving
        \item Assessment of project dependencies and constraints
        \item Time management
        \item Project Planning and Management
        \item Detail \& Result oriented
        \item Fast learner
    \end{itemize}
\end{minipage}
\cvsect{Skills (Expanded)}
\begin{minipage}[t]{1\textwidth}
    \begin{minipage}[t]{.085\textwidth}
    \end{minipage}
    \hfill
     \begin{minipage}[t]{.4575\textwidth}
           \begin{itemize}[itemsep=2pt,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=0pt]
            \item Familiar with a variety of database tools and schemas.
            \item Excellent debugging and memory profiling skills.
             \item Experienced with various data structures and algorithms.
            \item Familiar with data modeling techniques and their applications.

            \item Experienced with memory management techniques in C family languages, and pointer arithmetic/manipulation.
            \item Experience using UML diagrams and other high level planning, design, and analysis tools.
        \end{itemize}
    \end{minipage}
    \hfill
     \begin{minipage}[t]{.48\textwidth}
        \begin{itemize}[itemsep=2pt,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=0pt]
            \item Excellent written and verbal communication skills.
            \item Experienced with Generic Programming techniques.
            \item Solid understanding of network architecture and design.
            \item Capable of reading Assembly when debugging programs.
            \item Excellent problem solving skills in various languages.
            \item Log based debugging of SQL Databases and Java/Kotlin Apps.
            \item Excellent skills in applied Discrete Mathematics.
            \item Experienced with Object Oriented and Functional programming.
        \end{itemize}
    \end{minipage}
\end{minipage}
\end{document}
